\ZpL: a p-adic precision package

### 2018-01-31 ZpL/ZpL.tex
Examples shortened: small font + ZpFP removed

@@

We begin our tour of the features of the \ZpL package
with some basic arithmetic computations.
The first step is the definition of the $p$-adic ring or field.
\begin{tabular}{rl}
\cIn
 & \verb?Z3 = Zp(3, prec=20, print_mode="digits")? \\
\end{tabular}
It means that we will work in various implementation of the 
ring of $3$-adic integers with $20$ digits
of precision. 
We show the results for \ZpCR, \ZpFP and \ZpLC.
Results for \ZpLF are only shown when they differ from \ZpLC.
We first take some random element $x$.
\begin{tabular}{rl}
\cIn
 & \verb?x = random_element(Z3,5)? \\
 & \verb?x? \\
\cZpCR
 & \verb?...11111? \\
\cZpFP
 & \verb?...00000000000000011111? \\
\cZpLC
 & \verb?...11111? \\
\end{tabular}
Multiplication by $3$ is a shift on the digits, whether it 
is done by addition or multiplication.

\begin{tabular}{rl}
\cIn
 & \verb?3*x? \\
\cZpCR
 & \verb?...111110? \\
\cZpFP
 & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? \\
\cIn
 & \verb?x + x + x? \\
\cZpCR
 & \verb?...11110? \\
\cZpFP
 & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? \\
\end{tabular}

Something is lost however in \ZpCR when performing
$x+2x.$

\begin{tabular}{rl}
\cIn
 & \verb?y = 2*x? \\
 & \verb?y? \\
\cZpCR
 & \verb?...22222? \\
\cZpFP
 & \verb?...00000000000000022222? \\
\cZpLC
 & \verb?...22222? \\
\cIn
 & \verb?x + y? \\
\cZpCR
 & \verb?...11110? \\
\cZpFP
 & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? \\
\end{tabular}

The same phenomenon occurs when comparing the computation
of $x^3$ and $x \times x^2.$

\begin{tabular}{rl}
\cIn
 & \verb?x^3? \\
\cZpCR
 & \verb?...010101? \\
\cZpFP
 & \verb?...00000010100000010101? \\
\cZpLC
 & \verb?...010101? \\
\cIn
 & \verb?y = x^2? \\
 & \verb?x * y? \\
\cZpCR
 & \verb?...10101? \\
\cZpFP
 & \verb?...00000010100000010101? \\
\cZpLC
 & \verb?...010101? \\

\end{tabular}

@@

\begin{tabular}{rl}
\cIn
 & \verb?x = random_element(Z2,10)? \\
 & \verb?y = random_element(Z2,5)? \\
\cIn
 & \verb?u = x+y? \\
 & \verb?u? \\
\cZpCR
 & \verb?...10111? \\
\cZpFP
 & \verb?...000000000000000000000011010111? \\
\cZpLC
 & \verb?...10111? \\
\cIn
 & \verb?v = x-y? \\
 & \verb?v? \\
\cZpCR
 & \verb?...01111? \\
\cZpFP
 & \verb?...000000000000000000000011001111? \\
\cZpLC
 & \verb?...01111? \\
\end{tabular}

Now, let us compute $u+v=2 \times x.$

\begin{tabular}{rl}
\cIn
 & \verb?u+v? \\
\cZpCR
 & \verb?...00110? \\
\cZpFP
 & \verb?...0000000000000000000000110100110? \\
\cZpLC
 & \verb?...00110100110? \\
\cIn
 & \verb?2*x? \\
\cZpCR
 & \verb?...00110100110? \\
\cZpFP
 & \verb?...0000000000000000000000110100110? \\
\cZpLC
 & \verb?...00110100110? \\
\end{tabular}

No loss in precision appears in \ZpLC, contrary to \ZpCR.
We remark that \ZpFP also provides all the correct digits.

@@

\begin{tabular}{rl}
\cIn
 & \verb?Q2 = Zp(2, prec=10, print_mode="digits")? \\
 & \verb?MS = MatrixSpace(Q2,3,3)? \\
 & \verb?Mat = MS.random_element()? \\
 & \verb?chi = Mat.charpoly()? \\
 & \verb?deto = Mat.determinant()? \\
 & \verb?deto? \\
\cZpCR
 & \verb?...000100000100? \\
\cZpFP
 & \verb? ...11010101010? \\
\cZpLC
 & \verb?  ...0110110001? \\
\cZpLF
 & \verb?...001110111100? \\
\end{tabular}

\begin{tabular}{rl}
\cIn
 & \verb?chi? \\
\cZpCR
 & \verb?(...0000000001)*x^3 + (...1001111111)*x^2 ?\\
 & \verb?+ (...01110101110)*x + (...111011111100)? \\
\cZpFP
 & \verb?...0000000001*x^3 + ...1101001001*x^2 + ?\\
 & \verb?...0100110011*x + ...00101010110? \\
\cZpLC
 & \verb?...0000000001*x^3 + ...1011000111*x^2 + ?\\
 & \verb?...0011101000*x + ...1001001111? \\
\cZpLF
 & \verb?...0000000001*x^3 + ...1111000101*x^2 + ?\\
 & \verb?...0011111111*x + ...110001000100? \\
\end{tabular}

@@

\begin{tabular}{rl}
\cIn
 & \verb?Z2 = Zp(2, prec=15, print_mode="digits")? \\
  & \verb?S.<x> = PolynomialRing(Z2)? \\
 & \verb?P = random_element(S, degree=10, prec=5)? \\
 & \verb?Q = random_element(S, degree=10, prec=5)? \\
 & \verb?D = x^5 + random_element(S, degree=4, prec=8)? \\
 & \verb?def euclidean(A,B):? \\
 & \verb?    while B != 0:? \\
 & \verb?        A, B = B, A % B? \\
 & \verb?    return A.monic()? \\
\end{tabular}

\begin{tabular}{rl}
\cIn
  & \verb?euclidean(D*P, D*Q)? \\
\cZpCR
 & \verb?(...1)*x^9 + (0)*x^8 + (...,.1)*x^7 ?\\
 & \verb?+ (...,.1)*x^6 + (...1)*x^5 + (...1)*x^4?\\
 & \verb? + (...,.1)*x^3 + (0)*x^2 + (...,.1)*x + (...10)? \\
\cZpFP
 & \verb?...000000000000000000000000000001? \\
\cZpLC
 & \verb?...1*x^5+...100*x^3+...100*x^2+...1*x+...1? \\
\end{tabular}

@@

\begin{tabular}{rl}
\cIn
 & \verb?def somos4(u0, u1, u2, u3, n):? \\
 & \verb?    a, b, c, d = u0, u1, u2, u3? \\
 & \verb?    for _ in range(4, n+1):? \\
 & \verb?        a, b, c, d = b, c, d, (b*d + c*c) / a? \\
 & \verb?    return d? \\
\end{tabular}
\begin{tabular}{rl}
\cIn
 & \verb?somos4(Z2(1,15), Z2(1,15), Z2(1,15), Z2(3,15), 18)? \\
\cZpCR
 & \verb?...11? \\
\cZpFP
 & \verb?...110111001000100100000000000111? \\
\cZpLC
 & \verb?...100000000000111? \\
\cIn
 & \verb?somos4(Z2(1,15), Z2(1,15), Z2(1,15), Z2(3,15), 100)? \\
\cZpCR
 & \verb?PrecisionError: cannot divide by something?\\
 &\verb?indistinguishable from zero.? \\
\cZpFP
 & \verb?...110000101000011001001001110001? \\
\cZpLC
 & \verb?...001001001110001? \\
\end{tabular}
%
%\begin{tabular}{|l|l|}
%\verb?R = Zp(2)? & \verb?R = ZpL(2)? \\
%\multicolumn{2}{|l|}{\tt x, y, z, t = R(1,15), R(1,15), R(1,15), R(3,15)} \\
%\multicolumn{2}{|l|}{\tt for \_ in range(20):} \\
%\multicolumn{2}{|l|}{\tt \ \ \ \ x, y, z, t = y, z, t, (y*t + z*z)/x} \\
%\multicolumn{2}{|l|}{\tt \ \ \ \ print t} \\
%\hfill\verb?...000000000000100? & \hfill\verb?...000000000000100? \\
%\hfill\verb?...000000000001101? & \hfill\verb?...000000000001101? \\
%\hfill\verb?...000000000110111? & \hfill\verb?...000000000110111? \\
%\hfill\verb?...101010111010111? & \hfill\verb?...101010111010111? \\
%\hfill\verb?...1100111101111? & \hfill\verb?...101100111101111? \\
%\hfill\verb?...1110000010010? & \hfill\verb?...111110000010010? \\
%\hfill\verb?...0001000111001? & \hfill\verb?...100001000111001? \\
%\hfill\verb?...0000011111101? & \hfill\verb?...100000011111101? \\
%\hfill\verb?...1000000110101? & \hfill\verb?...001000000110101? \\
%\hfill\verb?...101101010011? & \hfill\verb?...010101101010011? \\
%\hfill\verb?...110000000000? & \hfill\verb?...001110000000000? \\
%\hfill\verb?...000101011101? & \hfill\verb?...111000101011101? \\
%\hfill\verb?...001001101011? & \hfill\verb?...111001001101011? \\
%\hfill\verb?...000011110011? & \hfill\verb?...111000011110011? \\
%\hfill\verb?...11? & \hfill\verb?...0000000111? \\
%\hfill\verb?...10? & \hfill\verb?...1010001110? \\
%\hfill\verb?...01? & \hfill\verb?...1110110001? \\
%\hfill\verb?...01? & \hfill\verb?...011110111001? \\
%\hfill\verb?...01? & \hfill\verb?...100101101001001? \\
%\hfill\verb?...1? & \hfill\verb?...11111000011? \\
%\end{tabular}
%
%\begin{itemize}
%\item SOMOS sequence
%\item many multiplications of matrices
%\item Dodgson algorithm
%\item subresultants
%\item Grobner basis
%\item $p$-adic differential equations
%\end{itemize}

@@

\begin{tabular}{rl}
\cIn
 & \verb?Z2 = Zp(2, prec=100)? \\
 & \verb?MS2 = MatrixSpace(Z2,2,2)? \\
 & \verb?Mat = random_element(MS2,prec=5)? \\
 & \verb?for _ in range(100):? \\
 & \verb?    Mat = Mat*random_element(MS2, prec=5)? \\
 & \verb?Mat? \\
\cZpCR
 & \verb?[ O(2^9) O(2^11)]? \\
 & \verb?[ O(2^9) O(2^11)]? \\
\cZpLC
 & \verb?[2^9 + 2^10 + 2^11 + O(2^12)  O(2^14)]? \\
 & \verb?[       2^9 + 2^11 + O(2^12)  O(2^14)]? \\
\end{tabular}

\ZpL can count the number of diffusede digits.

\begin{tabular}{rl}
\cIn
 & \verb?Z2.precision().number_of_diffused_digits()? \\
\cZpLC
 & \verb?604? \\
\end{tabular}

@@

\begin{tabular}{rl}
\cIn
 & \verb?Q2 = Qp(2, prec=50, print_mode="digits")? \\
 & \verb?R.<x,y,z> = PolynomialRing(Q2, order = 'invlex')? \\
 & \verb?F = [Q2(2,10)*x + Q2(1,10)*z, ? \\
 & \verb?     Q2(1,10)*x^2 + Q2(1,10)*y^2 - Q2(2,10)*z^2,? \\
 & \verb?     Q2(4,10)*y^2 + Q2(1,10)*y*z + Q2(8,10)*z^2]? \\
 & \verb?from sage.rings.polynomial.toy_buchberger?\\
 &\verb?  import buchberger_improved? \\
 & \verb?g = buchberger_improved(ideal(F)); g.sort()? \\
 & \verb?g? \\
\cZpCR
 & \verb?[x^3, x*y + ...1100010*x^2, y^2 + ...11001*x^2,? \\
 & \verb? z + ...0000000010*x]? \\
\cZpLC
 & \verb?[[x^3, x*y + ...111100010*x^2,? \\
 & \verb?y^2 + ...1111111001*x^2, z + ...0000000010*x]]? \\
\end{tabular}

As we can see, some loss in precision occurs in the
Buchberger algorithm and is avoided thanks to \ZpL.
Had we used \ZpFP, many padded zeroes or one would have appeared.

@@

\begin{tabular}{rl}
\cIn
 & \verb?N = 4? \\
 & \verb?Z2 = Zp(2, prec=50, print_mode="digits")? \\
 & \verb?Q2=Z2.fraction_field()? \\
 & \verb?S.<t> = PowerSeriesRing(Q2, 2^N)? \\
 & \verb?h = 1 + t + t^3? \\
 & \verb?y = t + t^2 * random_element(S,10)? \\
 & \verb?g = y.derivative() / h(y)? \\
 & \verb?u = Newton_Iteration_Solver(g, h, N)? \\
 & \verb?u[15]? \\
\cZpCR
 & \verb?...1101? \\
\cZpLC
 & \verb?...11011101? \\
\end{tabular}

@@

\begin{tabular}{rl}
\cIn
 & \verb?R = Qp(3,50)? \\
 & \verb?A.<x> = PolynomialRing(R)? \\
 & \verb?m=67? \\
 & \verb?g=1+(1/4)*x^2+x^6? \\
 & \verb?h=1+((m^2)/4)*x^2+m^6* x^6? \\
 & \verb?y=Lercier_Sirvent(g,h,6)? \\
 & \verb?y[31]? \\
 & \verb?u = Newton_Iteration_Solver(g, h, N)? \\
 & \verb?u[15]? \\
\cZpCR
 & \verb?(467995903278061284942799/3^14 + O(3^36))*x^31? \\
\cZpLC
 & \verb?(467995903278061284942799/3^14 + O(3^36))*x^31? \\
\end{tabular}

>>>>

We begin our tour of the features of the \ZpL package
with some basic arithmetic computations.
The first step is the definition of the $p$-adic ring or field.

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?Z2 = Zp(2, print_mode="digits")? \\
 & \verb?Q2 = Qp(2, print_mode="digits")? \\
\end{tabular}}

\noindent
It means that we will work in various implementation of the 
ring of $2$-adic integers with $20$ digits of precision (which
is the default).
The rings \verb?Z3? and \verb?Q3? are defined similarly.

We show the results for \ZpCR%, \ZpFP 
and \ZpLC.
Results for \ZpLF are only shown when they differ from \ZpLC.

@@

We first take some random element $x$.

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?x = random_element(Z3,5)? \\
 & \verb?x? \\
\cZpCR
 & \verb?...11111? \\
%\cZpFP
% & \verb?...00000000000000011111? \\
\cZpLC
 & \verb?...11111? \\
\end{tabular}}

Multiplication by $3$ is a shift on the digits, whether it 
is done by addition or multiplication.

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?3*x? \\
\cZpCR
 & \verb?...111110? \\
%\cZpFP
% & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? \\
\cIn
 & \verb?x + x + x? \\
\cZpCR
 & \verb?...11110? \\
%\cZpFP
% & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? \\
\end{tabular}}

Something is lost however in \ZpCR when performing $x+2x$.

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?y = 2*x; y? \\
\cZpCR
 & \verb?...22222? \\
%\cZpFP
% & \verb?...00000000000000022222? \\
\cZpLC
 & \verb?...22222? \\
\cIn
 & \verb?x + y? \\
\cZpCR
 & \verb?...11110? \\
%\cZpFP
% & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? \\
\end{tabular}}

The same phenomenon occurs when comparing the computation
of $x^3$ and $x \times x^2$.

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?x^3? \\
\cZpCR
 & \verb?...010101? \\
%\cZpFP
% & \verb?...00000010100000010101? \\
\cZpLC
 & \verb?...010101? \\
\cIn
 & \verb?y = x^2? \\
 & \verb?x * y? \\
\cZpCR
 & \verb?...10101? \\
%\cZpFP
% & \verb?...00000010100000010101? \\
\cZpLC
 & \verb?...010101? \\
\end{tabular}}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?x = random_element(Z2,10)? \\
 & \verb?y = random_element(Z2,5)? \\
\cIn
 & \verb?u = x+y? \\
 & \verb?u? \\
\cZpCR
 & \verb?...10111? \\
%\cZpFP
% & \verb?...000000000000000000000011010111? \\
\cZpLC
 & \verb?...10111? \\
\cIn
 & \verb?v = x-y? \\
 & \verb?v? \\
\cZpCR
 & \verb?...01111? \\
%\cZpFP
% & \verb?...000000000000000000000011001111? \\
\cZpLC
 & \verb?...01111? \\
\end{tabular}}

Now, let us compute $u+v$ (and observe that it is actually equal to $2x$).

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?u+v? \\
\cZpCR
 & \verb?...00110? \\
%\cZpFP
% & \verb?...0000000000000000000000110100110? \\
\cZpLC
 & \verb?...00110100110? \\
\cIn
 & \verb?2*x? \\
\cZpCR
 & \verb?...00110100110? \\
%\cZpFP
% & \verb?...0000000000000000000000110100110? \\
\cZpLC
 & \verb?...00110100110? \\
\end{tabular}}

No loss in precision appears in \ZpLC, contrary to \ZpCR.
%We remark that \ZpFP also provides all the correct digits.

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?M = random_element(MatrixSpace(2,2), prec=10)? \\
 & \verb?M.determinant()? \\
\cZpCR
 & \verb?...000100000100? \\
%\cZpFP
% & \verb? ...11010101010? \\
\cZpLC
 & \verb?  ...0110110001? \\
\cZpLF
 & \verb?...001110111100? \\
\cIn
 & \verb?M.charpoly()? \\
\cZpCR
 & \verb?(...0000000001)*x^3 + (...1001111111)*x^2 ?\\
 & \verb?+ (...01110101110)*x + (...111011111100)? \\
%\cZpFP
% & \verb?...0000000001*x^3 + ...1101001001*x^2 + ?\\
% & \verb?...0100110011*x + ...00101010110? \\
\cZpLC
 & \verb?...0000000001*x^3 + ...1011000111*x^2 + ?\\
 & \verb?...0011101000*x + ...1001001111? \\
\cZpLF
 & \verb?...0000000001*x^3 + ...1111000101*x^2 + ?\\
 & \verb?...0011111111*x + ...110001000100? \\
\end{tabular}}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?S.<x> = PolynomialRing(Z2)? \\
 & \verb?P = random_element(S, degree=10, prec=5)? \\
 & \verb?Q = random_element(S, degree=10, prec=5)? \\
 & \verb?D = x^5 + random_element(S, degree=4, prec=8)? \\
\cIn
 & \verb?def euclidean(A,B):? \\
 & \verb?    while B != 0:? \\
 & \verb?        A, B = B, A % B? \\
 & \verb?    return A.monic()? \\
\cIn
  & \verb?euclidean(D*P, D*Q)? \\
\cZpCR
 & \verb?(...1)*x^9 + (0)*x^8 + (...,.1)*x^7 ?\\
 & \verb?+ (...,.1)*x^6 + (...1)*x^5 + (...1)*x^4?\\
 & \verb? + (...,.1)*x^3 + (0)*x^2 + (...,.1)*x + (...10)? \\
%\cZpFP
% & \verb?...000000000000000000000000000001? \\
\cZpLC
 & \verb?...1*x^5+...100*x^3+...100*x^2+...1*x+...1? \\
\end{tabular}}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?def somos4(u0, u1, u2, u3, n):? \\
 & \verb?    a, b, c, d = u0, u1, u2, u3? \\
 & \verb?    for _ in range(4, n+1):? \\
 & \verb?        a, b, c, d = b, c, d, (b*d + c*c) / a? \\
 & \verb?    return d? \\
\cIn
 & \verb?u0 = u1 = u2 = Z2(1,15); u3 = Z2(3,15)? \\
 & \verb?somos4(u0, u1, u2, u3, 18)? \\
\cZpCR
 & \verb?...11? \\
%\cZpFP
% & \verb?...110111001000100100000000000111? \\
\cZpLC
 & \verb?...100000000000111? \\
\cIn
 & \verb?somos4(u0, u1, u2, u3, 100)? \\
\cZpCR
 & \verb?PrecisionError: cannot divide by something?\\
 &\verb?indistinguishable from zero.? \\
%\cZpFP
% & \verb?...110000101000011001001001110001? \\
\cZpLC
 & \verb?...001001001110001? \\
\end{tabular}}

%
%\begin{tabular}{|l|l|}
%\verb?R = Zp(2)? & \verb?R = ZpL(2)? \\
%\multicolumn{2}{|l|}{\tt x, y, z, t = R(1,15), R(1,15), R(1,15), R(3,15)} \\
%\multicolumn{2}{|l|}{\tt for \_ in range(20):} \\
%\multicolumn{2}{|l|}{\tt \ \ \ \ x, y, z, t = y, z, t, (y*t + z*z)/x} \\
%\multicolumn{2}{|l|}{\tt \ \ \ \ print t} \\
%\hfill\verb?...000000000000100? & \hfill\verb?...000000000000100? \\
%\hfill\verb?...000000000001101? & \hfill\verb?...000000000001101? \\
%\hfill\verb?...000000000110111? & \hfill\verb?...000000000110111? \\
%\hfill\verb?...101010111010111? & \hfill\verb?...101010111010111? \\
%\hfill\verb?...1100111101111? & \hfill\verb?...101100111101111? \\
%\hfill\verb?...1110000010010? & \hfill\verb?...111110000010010? \\
%\hfill\verb?...0001000111001? & \hfill\verb?...100001000111001? \\
%\hfill\verb?...0000011111101? & \hfill\verb?...100000011111101? \\
%\hfill\verb?...1000000110101? & \hfill\verb?...001000000110101? \\
%\hfill\verb?...101101010011? & \hfill\verb?...010101101010011? \\
%\hfill\verb?...110000000000? & \hfill\verb?...001110000000000? \\
%\hfill\verb?...000101011101? & \hfill\verb?...111000101011101? \\
%\hfill\verb?...001001101011? & \hfill\verb?...111001001101011? \\
%\hfill\verb?...000011110011? & \hfill\verb?...111000011110011? \\
%\hfill\verb?...11? & \hfill\verb?...0000000111? \\
%\hfill\verb?...10? & \hfill\verb?...1010001110? \\
%\hfill\verb?...01? & \hfill\verb?...1110110001? \\
%\hfill\verb?...01? & \hfill\verb?...011110111001? \\
%\hfill\verb?...01? & \hfill\verb?...100101101001001? \\
%\hfill\verb?...1? & \hfill\verb?...11111000011? \\
%\end{tabular}
%
%\begin{itemize}
%\item SOMOS sequence
%\item many multiplications of matrices
%\item Dodgson algorithm
%\item subresultants
%\item Grobner basis
%\item $p$-adic differential equations
%\end{itemize}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
% & \verb?Z2 = Zp(2, prec=100)? \\
 & \verb?MS = MatrixSpace(Z2,2)? \\
 & \verb?M = random_element(MS, prec=5)? \\
 & \verb?for _ in range(100):? \\
 & \verb?    M *= random_element(MS, prec=5)? \\
 & \verb?M? \\
\cZpCR
 & \verb?[ O(2^9) O(2^11)]? \\
 & \verb?[ O(2^9) O(2^11)]? \\
\cZpLC
 & \verb?[2^9 + 2^10 + 2^11 + O(2^12)  O(2^14)]? \\
 & \verb?[       2^9 + 2^11 + O(2^12)  O(2^14)]? \\
\end{tabular}}

%\ZpL can count the number of diffused digits.
%\begin{tabular}{rl}
%\cIn
% & \verb?Z2.precision().number_of_diffused_digits()? \\
%\cZpLC
% & \verb?604? \\
%\end{tabular}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
% & \verb?Q2 = Qp(2, prec=50, print_mode="digits")? \\
 & \verb?R.<x,y,z> = PolynomialRing(Q2, order = 'invlex')? \\
 & \verb?F = [ Q2(2,10)*x + Q2(1,10)*z, ? \\
 & \verb?      Q2(1,10)*x^2 + Q2(1,10)*y^2 - Q2(2,10)*z^2,? \\
 & \verb?      Q2(4,10)*y^2 + Q2(1,10)*y*z + Q2(8,10)*z^2 ]? \\
\cIn
 & \verb?from sage.rings.polynomial.toy_buchberger\?\\
 & \verb?    import buchberger_improved? \\
 & \verb?g = buchberger_improved(ideal(F)); g.sort()? \\
 & \verb?g? \\
\cZpCR
 & \verb?[x^3, x*y + ...1100010*x^2,? \\
 & \verb? y^2 + ...11001*x^2, z + ...0000000010*x]? \\
\cZpLC
 & \verb?[x^3, x*y + ...111100010*x^2,? \\
 & \verb? y^2 + ...1111111001*x^2, z + ...0000000010*x]? \\
\end{tabular}}

As we can see, some loss in precision occurs in the
Buchberger algorithm and is avoided thanks to \ZpL.
%Had we used \ZpFP, many padded zeroes or one would have appeared.

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
% & \verb?N = 4? \\
% & \verb?Z2 = Zp(2, prec=50, print_mode="digits")? \\
% & \verb?Q2=Z2.fraction_field()? \\
 & \verb?S.<t> = PowerSeriesRing(Q2, 16)? \\
 & \verb?h = 1 + t + t^3? \\
 & \verb?y = t + t^2 * random_element(S,10)? \\
 & \verb?g = y.derivative() / h(y)? \\
 & \verb?u = Newton_Iteration_Solver(g, h, 4)? \\
 & \verb?u[15]? \\
\cZpCR
 & \verb?...1101? \\
\cZpLC
 & \verb?...11011101? \\
\end{tabular}}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?R = Qp(3,50)? \\
 & \verb?A.<x> = PolynomialRing(R)? \\
 & \verb?m = 67? \\
 & \verb?g = 1 + (1/4)*x^2 + x^6? \\
 & \verb?h = 1 + ((m^2)/4)*x^2 + m^6*x^6? \\
 & \verb?y = Lercier_Sirvent(g, h, 6)? \\
 & \verb?y[31]? \\
 & \verb?u = Newton_Iteration_Solver(g, h, N)? \\  % ???
 & \verb?u[15]? \\
\cZpCR
 & \verb?(467995903278061284942799/3^14 + O(3^36))*x^31? \\
\cZpLC
 & \verb?(467995903278061284942799/3^14 + O(3^36))*x^31? \\
\end{tabular}}
